---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(dplyr)
library(here)
here::here()
```
# reading clean data from clean data folder
```{r}
clean_candy <- read_csv(here("clean_data/clean_candy_15_16_17.csv"))

```
 
#Q1-What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

```{r}
clean_candy %>% 
  select(ratings) %>% 
  summarise(total_no = sum(!is.na(ratings)))

```

# Q2-What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?
```{r}
clean_candy %>%  
  mutate(age, age = (as.numeric(age))) %>% 
  filter(age > 0 & age < 150) %>% # to get rid of any unkowing value
  group_by(going_trick_or_treating) %>% 
summarise(ave = mean(age))

```




# Q3-For each of joy, despair and meh, which candy bar received the most of these ratings?
```{r}
clean_candy %>% 
  group_by(ratings) %>% 
summarise(no_ratings = n()) %>% 
  slice_max(no_ratings)
```
# Q4-How many people rated Starburst as despair?
```{r}
clean_candy %>% 
  filter(candy == "starburst" ,ratings == "DESPAIR") %>% 
  group_by(ratings) %>% 
  summarise(no_of_rated = n())
```

# mutation for despair as -1, joy as +1 and meh as 0. to be ready for the next Qs
```{r}
clean_candy <- clean_candy %>% 
  mutate(new_rating = ifelse(ratings == "DESPAIR", -1,
               ifelse(ratings == "JOY",1 ,
                 ifelse(ratings == "MEH",0,"no"      
                      ))),
         new_rating = as.numeric(new_rating))
clean_candy
```


# Q6-What was the most popular candy bar by this rating system for each gender in the dataset?
```{r}
clean_candy %>% 
  group_by(gender) %>% 
 summarise(most_pop_candy = sum(new_rating, na.rm = TRUE)) %>% 
  arrange(desc(most_pop_candy))
```
# Q7- What was the most popular candy bar in each year?
```{r}

clean_candy %>% 
  group_by(year) %>% 
 summarise(most_pop_candy = sum(new_rating, na.rm = TRUE)) %>% 
  arrange(desc(most_pop_candy))

```
# Q8-What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?
```{r}
clean_candy %>% 
  group_by(country) %>% 
 summarise(most_pop_candy = sum(new_rating, na.rm = TRUE)) %>% 
  arrange(desc(most_pop_candy))

```

