---
title: "Task 2"
output:
  html_document:
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: yes
---
```{r message=FALSE, echo=FALSE}
library(tidyverse)
library(janitor)
library(dplyr)
library(here)
```
# A brief introduction to the dataset
There are two dataset being used in this task, one is a cake dataset which continue all cakes and its ingredient being used in each cake. The ingredients names here in this dataset is a code for example, BR code meaning butter. The second dataset has all the ingredient names and its code that used in the first dataset.

# Assumptions
* First delete any column that all values are NA, which meaning that this ingredient didn’t use in any cake in the cake dataset.
* Delete the code from the code dataset if did not use in first set (if find any column that its value NA).
* Turn all NA to the number 0 which still meaning that this ingredient did not use in that cake(0 amount). The reason for that to improve the show of the dataset.

# The steps used to clean the data
* First reading the cake data from the row data file by using here method then trying to find all column that all variable not NA by sapply function.
* select these column from step 1 which at least the column has one value.
* Replace all NA into 0 by  _replace(is.na(.), 0)_
* Reading the second set which has the actual code name and measures.
* select the column code (names) from cake table in order to replace the code by actual names from the cake ingredient code dataset.
* Filter the ingredient code set which will keep only the one use needed.
*Writing the clean data to our folder clean data to be ready for the analysis.

# Analysis questions
## Reading the clean datasets from clean data folder
### reading the cake dataset 
```{r echo=FALSE, message=FALSE }
clean_cake <- read_csv(here("clean_data/clean_cake-ingredients-1961.csv"))
clean_cake
```

### Reading the cake ingreadient code  
```{r echo=FALSE, message=FALSE }
clean_cake_ingr_code <- read_csv(here("clean_data/clean_cake_ingredient_code.csv"))
clean_cake_ingr_code
```
## Q1 Which cake has the most cocoa in it?
```{r echo=FALSE}
clean_cake %>% 
  select(cake,cocoa) %>% 
  filter(cocoa == max(cocoa))
```

## Q2 For sponge cake, how many cups of ingredients are used in total?
```{r echo=FALSE}
#Q2 For sponge cake, how many cups of ingredients are used in total?
# below will select only ingredient that measure by cup from cake ingredient code table
measure_by_cup <- clean_cake_ingr_code %>% 
  filter(measure == "cup") %>% 
  select(ingredient) %>% 
  pull()
 
```

```{r echo=FALSE, message=FALSE}
# now will use from previous chunck the ingredient use cup for mesurement to find out how many
# cup used in sponge cake
clean_cake %>% 
  select(cake, measure_by_cup) %>% 
  filter(cake == "Sponge") %>%
   summarise(cake, total_cups = rowSums(.[-1]))
```

## Q3 How many ingredients are measured in teaspoons?
```{r echo=FALSE}
 measure_by_teaspoons <- clean_cake_ingr_code %>% 
 filter(measure == "teaspoon") %>%
  summarise( ingredients_by_teaspoon = n())
measure_by_teaspoons
```
## Q4 Which cake has the most unique ingredients?
```{r echo=FALSE}
clean_cake %>% 
pivot_longer("almond_essence":"zwiebach", names_to = "ingredient", values_to = "amount") %>% 
  filter(amount != 0) %>% 
  group_by(cake) %>% 
  summarise(ingredients_used = n())  %>% 
  slice_max(ingredients_used)
 
```

## Q5 Which ingredients are used only once?

```{r echo=FALSE}
clean_cake %>% 
pivot_longer("almond_essence":"zwiebach", names_to = "ingredient", values_to = "amount") %>% 
  filter(amount != 0) %>% 
  group_by(ingredient) %>% 
  summarise(total_use = n()) %>% 
  slice_min(total_use)

```



